---
title: "First_draft_group5"
output: html_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(data.table)
library(magrittr)
library(splines)
library(car)
library(effects)
library(dplyr)

# read the data
dt = fread("cleaned_data.csv")
analysis_dt = fread("cleaned_data.csv")
```

# Introduction

According to the American Time Use Survey (ATUS, https://www.bls.gov/charts/american-time-use/activity-by-work.htm), 85.8 percent of males and 66.5 percent of females work more than 40 hours per week in the U.S. Working overtime has been associated with diverse health problems, especially ischemic heart diseases and cerebrovascular diseases (Nishiyama & Johnson, 1997). Therefore, this project aims to examine whether working overtime is associated with the blood pressure level using the National Health and Nutrition Examination Survey (NHANES) data. In order to produce sufficient estimation sample size, this study use a pooled data from the three two-year cycle data sets: 2011-2012, 2013-2014, and 2015-2016.

It is well known that various biological and environmental factors influence the blood pressure level (Lauer, 1993; Papathanasiou, 2015). To control for the potential influences of such factors, we have systematically reviewed the literature to select the important factors that might affect the abnormal blood pressure levels of the respondents. Final predictors included in the model were gender, age, body mass index (BMI), alcohol consumption level, hours of sleep, and history of smoking. These final predictors closely matched with those from other published studies that observed the association between work hours and blood pressure levels  (Hayashi, 1996; Nakamura et al. 2012).

In terms of defining the criteria for the key variables of interest, working overtime were defined as working more than 40 hours per week. For the additional logistic regression analyses, abnormal blood pressure was defined as having systolic blood pressure higher than 140mm Hg and diastolic blood pressure higher than 90mm Hg following the guide from the American Heart Association. 


# Data Selction and Cleaning

The study population are participants, aged 18 - 60 and employed, of The National 
Health and Nutrition Examination Survey (NHANES) program in three two-years cycles: 2011-2012, 2013-2014 and 2015-2016. Among them, 2011-2012 cycle consists of 2495 
sample size, 2013-2014 cycle contains 2819 and 2015-2016 cycle includes 2799. For 
the purpose of this study, we exclude people who are now taking prescription due 
to hypertension. The exclusion leads to huge amount of reduction to our sample 
size: there are 100 observations left for 2011-2012, 95 for 2013-2014 and 140 for 
2015-2016.

Among 335 total sample sizes, we picked variables through literature reviews and
group discussion. Dataset varies for each two-years cycle by the suffix in the name. 
2011-2012 is G, 2013-2014 is H, and 2015-2016 is I. For the convenience, the suffix
will be replaced by *. Variables chosen are listed below:

The measurements of blood pressure: Systolic blood pressure and Diastolic blood 
pressure from BPX_* dataset. Each blood pressure are measured in 3 trails, sometimes
4 trials,

working hours in the last week from OCQ_* dataset,

Body mass index from BMX_* dataset,

demographic data: age and gender from DEMO_* dataset,

Alchol use in the last 12 months: ALQ120Q for the quantity and ALQ120U to differentiate
unit of week, month or year, from ALQ_* dataset,

Smoked tobacco in last five days: SMQ681 in 2013-2016, and SMQ680 in 2011-2012, 
from SMQRTU_* dataset,

sleeping hours in working days: SLD012 in 2015-2016, and SLD010H for others from
SLQ_* dataset.

The cleaning process involves excluding missing values for complete case analysis,
and excludig cases where there are more than 2 trails blood pressure measurements 
missing. After the cleaning process, the sample size for this study is 238 in total.


# Method

This study will implement multiple regression on each type (systolic and diatolic) 
blood pressure against working hours controlled by all other variables to assess 
if working overtimes would causehigher blood pressure. Coefficients and their 
p-value on statistic significance are reported.

The response variable blood pressure will be the average value of blood pressures
measured in 3 trails (sometimes 4 if one trial is missing); working hours is encoded
into dichotomy variable where 1 stands for working more than 40 hours and 0 otherwise;
alchol drinks are converted to average drinks in a week, so values with unit month
is divided by 4.345 and 52.143 for values with unit year. 3 digits are preserved; 
due to the difference of encoding of sleep variable in 2015-2016 (it has 14 meaning 
more 14 hours, but this limit is 12 in 2011-2014), we recode all sleep hours that 
are more than 12 to 12 to keep the consistency in sample dataset.

The additional analysis involves adding interactions, transformations to our classical
linear model. Logistics regression is applied to solve the research question in 
a different thinking.

We use data.table package, dplyr package and python for the data preparation process.
The multiple regression is implemented in python, lm function and gls function in 
R.


## core analysis {.tabset .tabset-fade}

### R_data.table
As we have got a nice cleaned dataset, we want to visualize our data with pair plots first. As shown in the pair plots for the systolic blood pressure, specifically from the scatter plots, we can find that there are weak relations or almost no relations between the variables. Moreover, from the histograms, we can find that the all the variables seem not to be normally distributed. Athough the variable systolic blood pressure and the variable bmi approach to be normally distributed, they are still right skewed. In addition, as shown in the pair plots for the diatolic blood pressure, from the scatter plots, again, we can find that there are weak relations or almost no relations between the variables. Also, from the histograms, except that the variable diatolic blood pressure seems to be almost normally distributed (only a little bit left skewed), all the other variables are not normally distributed.
```{r matrix_plot}
pairs( ~avg_sys_bp + gender + age + bmi + sleep + smoke + workhrs +
         alchol, data = analysis_dt, main = "simple matrix plot for Systolic blood pressure")
```
```{r matrix plot}
pairs( ~avg_dia_bp + gender + age + bmi + sleep + smoke + workhrs +
         alchol, data = analysis_dt, main = "simple matrix plot for Diastolic blood pressure")
```
```{r histogram}
par( mfrow=c(3,2) )
hist(analysis_dt$avg_sys_bp)
hist(analysis_dt$avg_dia_bp)
hist(analysis_dt$age)
hist(analysis_dt$bmi)
hist(analysis_dt$sleep)
hist(analysis_dt$alchol)
```

After exploring the data through vizualizing with pair plots, we fit our linear regression models.

For the systolic blood pressure, we fit the model: 
$$
\begin{aligned}
 y &= \beta_{0} + \beta_{workhrs}*x_{workhrs} + \beta_{gender}*x_{gender} + \beta_{age}*x_{age} + \beta_{bmi}*x_{bmi} \notag\\
 &+ \beta_{sleep}*x_{sleep} + \beta_{smoke}*x_{smoke} + \beta_{avg\_alcohol\_freq\_wk}*x_{avg\_alcohol\_freq\_wk} + \epsilon
\end{aligned}
$$

And for diatolic blood pressure, we fit the model: 
$$
\begin{aligned}
 y &= \beta_{0} + \beta_{workhrs}*x_{workhrs} + \beta_{gender}*x_{gender} + \beta_{age}*x_{age} + \beta_{bmi}*x_{bmi} \notag\\
 &+ \beta_{sleep}*x_{sleep} +  \beta_{smoke}*x_{smoke} + \beta_{avg\_alcohol\_freq\_wk}*x_{avg\_alcohol\_freq\_wk} + \epsilon
\end{aligned}
$$

```{r models systolic bp}
## systolic bp
pre_sys_fit = lm(avg_sys_bp ~ gender + age + bmi + sleep + smoke + workhrs + alchol,
             data = analysis_dt)

summary(pre_sys_fit)
```
```{r models diatolic bp}
## diatolic bp
pre_dia_fit = lm(avg_dia_bp ~ gender + age + sleep + smoke + workhrs + alchol,
                 data = analysis_dt)
 
summary(pre_dia_fit)
```

From the summary results of the linear regression model for the systolic blood pressure, we can find that although the coefficient of the working hours is positive, which implies that working overtime increases the risk of high systolic blood pressure, this effect is not significant ($\beta = 1.58$, p = 0.557). As a result, we can conclude that working overtime cannot lead to abnormal systolic blood pressure. Besides, from the summary results of the linear regression model for the diatolic blood pressure, we can find that although the coefficient of the working hours is positive as well, which implies that working overtime increases the risk of high diatolic blood pressure too, this effect is not significant as well($\beta = 0.2246$, p = 0.905). As a result, we can conclude that working overtime also cannot lead to abnormal diatolic blood pressure. Therefore, in conclusion, working overtime also cannot lead to abnormal blood pressure.

After fitting the linear regression model, we want to check whether the following assumptions of the linear regression model are held:

1. Homoscedasticity: The variance of the residual is constant. 
2. Linearity: The relationship between between the independent and dependent variables is linear.
3. No or little multicollinearity: There is no or little collinearity between independent variables.

1. Homoscedasticity

In order to check the homoscedasticity assumption, we plotted residual plots for both systolic blood pressure and diatolic pressure.
```{r residuals plot}
par( mfrow=c(1,2) )
## standardized residuals plot for systolic bp
st_sys_red = rstandard(pre_sys_fit)
fitted_sys = pre_sys_fit$fitted.values

plot(fitted_sys, st_sys_red, xlab = "fitted values", 
     ylab = "standardized residuals", 
     main = "standardized residuals plot (systolic bp)")

## standardized residuals plot for diatolic bp
st_dia_red = rstandard(pre_dia_fit)
fitted_dia = pre_sys_fit$fitted.values

plot(fitted_dia, st_dia_red, xlab = "fitted values", 
     ylab = "standardized residuals", 
     main = "standardized residuals plot (diatolic bp)")
```
From the residual plot of the systolic blood pressure, we can find the mean of the residual is almost 0, and the variance seems to be almost constant. Also, we have the same finds for the diatolic blood pressure. Therefore, the assumption of homoscedasticity can be considered as satisfied.

2. No or little multicollinearity

In order to check the no/little-multicollinearity assumption, we computed the Pearson correlations between the continuous independent variables and Chi-squared correlation test between the binary independent variables.
```{r dt continuous correlations}
cov_mat = vcov(pre_sys_fit)
cov_mat[-1, -1] 
```
```{r dt factors correlations}
## check correlation between indicators
gs = chisq.test(analysis_dt$gender, analysis_dt$smoke)
gw = chisq.test(analysis_dt$gender, analysis_dt$workhrs)
sw = chisq.test(analysis_dt$smoke, analysis_dt$workhrs)

## make tables
row = c("gender", "gender", "smoke")
col = c("smoke", "workhrs", "workhrs")
chi_sq_stats = c( gs$statistic, gw$statistic, sw$statistic )
p_value = c(gs$p.value, gw$p.value, sw$p.value)

m = as.data.table(cbind(row, col, chi_sq_stats, p_value))
m
```
As shown in the heatmap of the correlations between the continuous independent variables, we can find that there are very small or almost no correlations between the continuous independent variables. Also, as the table of the Pearson correlations between the binary variables shows, we can find that there is little collinearity between each pair of the binary variables.

3. Linearity

In order to check the linearity assumption, we plotted partial regression plots for both systolic blood pressure and diatolic pressure against each of the independent variables.
```{r check linearity systolic bp}
avPlots(pre_sys_fit)
```

```{r check linearity diatolic bp}
avPlots(pre_dia_fit)
```
From the partial regression plots of the systolic blood pressure, we can find that for each of the independent variable, the expected value of the dependent variable (systolic blood pressure) is indeed a straight-line function of the independent variable, holding the others fixed. Also, from the partial regression plots of the diatolic blood pressurewe, we can get the same conclusion. Therefore, the assumption of linearity can be considered as satisfied.


additional analysis 

After examing the mutiple linear regression in the core analysis, I'm interested in
a more complicated model considering intercations and transformations to adjust the 
non-linearity and non-constant variance.

The following model considers the logarithm of average systolic blood pressure. For
variables alchol and sleep, the model apply them into basis splines function with
degrees of freedom 5 and order of three, with 2 knots. Interaction effect between 
worhrs and all other variables are considered. The estimations and significance level
are reported in the following:
```{r}
fit_sys = lm( log(avg_sys_bp) ~ workhrs * (age + gender + bmi + bs(alchol, 5) + 
                                             bs(sleep, 5) + smoke) + smoke:alchol,
              data = dt)

summary(fit_sys)
AIC(fit_sys)
```
The model has R-squared 0.2317. The F-test against the null model calcutes the statistic 
of 2.081 with 30 and 207 degrees of freedom. The p-value is 0.00154, which suggests
the statistical significance of this model in 0.05 confidence level. The AIC of this
model is -252.428.

```{r}
vif(fit_sys)
```
When checking the variance inflation factor, I find that workhrs, workhrs:age, and
workhrs:bmi are greatly inflated (more than 5). It suggests that there might be 
significant effect of collinearity, which may unstable the coefficients estimations.

```{r}
par( mfrow = c(2,2) )
plot(Effect("age", fit_sys, partial.residuals = TRUE))
plot(Effect("bmi", fit_sys, partial.residuals = TRUE))
plot(Effect("alchol", fit_sys, partial.residuals = TRUE))
plot(Effect("sleep", fit_sys, partial.residuals = TRUE))
```
Above plots examine the effect of each continuous variables in the model on the 
response variable. The blue lines shows the relationship from the model. The red dots
are partial residuals and the red line shows how each variable correlates to the 
response variable after controlling all other variables. We see that our model dose
quite well on explaining the correlation for age, bmi and alchol. The basis spline 
function of Sleep, as we can see, become very unstable at the boundary points. This 
might suggests extrapolation bias.

The coefficients of this model is very hard to interpret, even though the model 
roughly satisfies the linear modeling assumptions. However, the model is still useful 
to explain several research questions. In the following example, I examine if sleep 
for 5 hours would cause significant difference on blood pressure than sleep for 8 hours
if they both work overtimes.

To answer the question, if we directly use the model, we need to consider interaction
terms on variables interested, and coefficients of basis splines transformation 
on sleep are more meaningful in mathematic rather than practical setting. 

The code below create two fake datasets accroding to the original dataset. One with
all sleep equals to 8 while the other equal to 5. Both dataset has workhrs as 1.
After combining the original dataset with two fake datasets, we assign weights 1 to
all original observations and zero to all fake observations. The purpose of assigning 
weights is to get the same coefficients with the previously fitted model and the 
same structure of the design matrix (same interactions and transformation, but with
fake data). Above steps help us to get the contrast value by applying the model 
coefficients to our data generated by test assumptions.
```{r}
# would difference between work overtimes but sleep for 8 hours and work overtimes 
# while sleep for 5 hours less significant?
dt = dt[, wgt := 1]

d_fake_8hrs = copy(dt)
d_fake_8hrs[, `:=` (workhrs = 1, sleep = 8, wgt = 0)] # make fake data with contrast

d_fake_5hrs = copy(dt)
d_fake_5hrs[, `:=` (workhrs = 1, sleep = 5, wgt = 0)] # make fake data with contrast

dx = rbindlist( list(dt, d_fake_8hrs, d_fake_5hrs) ) # combine tru data with fake data

result = lm( log(avg_sys_bp) ~ workhrs * (age + gender + bmi + bs(alchol, 5) + 
                                             bs(sleep, 5) + smoke) + smoke:alchol,
             weights = wgt, data = dx) # fit regression with zero weights on fake data

pa = coef(result) # parameters
cm = vcov(result) # covariance matrix
dm = model.matrix(result) # design matrix
nx = 238

ct = dm[ (nx+1):(nx+2*nx), ]
ct = ct[1:nx,] - ct[(nx+1):(2*nx), ] # get the contrast

znum = ct %*% pa # numerator of z-score
zdenom = sqrt(diag(ct %*% cm %*% t(ct))) # denominator of z-score
zscores = znum / zdenom

z_criticle = qnorm(0.975)

{mean(zscores) > z_criticle}
```
The z-score is 0.864, which is lesser than 1.96. We failed to reject the null hypothesis 
that sleep 5 hours would cause difference in blood pressur than sleep 8 hours if 
both people work overtimes.

### R_dplyr

```{r dplyr setup, include=FALSE}
#This script include initial and main analyses for the STATS506 group project.
#"Does working overtime predict abnormal blood pressure?"
#Author: Hyesue Jang

rm(list=ls())
library(dplyr)
library(tidyr) #for drop_na() function
library(nlme)

#read in data
df = read.csv("final_data.csv", header = TRUE)
df = as_tibble(df)

#names(df)
df = df %>% 
  mutate(
    #factor categorical variables
    gender = factor(df$gender, 
                    levels = c(1,2), 
                    labels = c("male","female")),
    alcohol_unit = factor(df$alcohol_unit,
                          levels = c(1,2,3),
                          labels = c("week", "month", "year")),
    smoke = factor(df$smoke,
                   levels = c(1,2),
                   labels = c("Smoked", "NotSmoked")),
    #compute overtime variable
    overtime = ifelse(workhrs > 40, 1, 0),
    #compute average BP measures
    SBP = rowMeans(cbind(BPXSY1, BPXSY2, BPXSY3, BPXSY4), na.rm = T),
    DBP = rowMeans(cbind(BPXDI1, BPXDI2, BPXDI3, BPXDI4), na.rm = T),
    #compute abnormal BP variables
    SBP_bi = ifelse(SBP < 140, 0, 1),
    DBP_bi = ifelse(DBP < 90, 0, 1)) %>%
  drop_na(c("SBP", "DBP"))
#remove those with incomplete BP measures 
df = quantable::removeNArows(df, 2)
#recode alcohol variables
#measure of units differ by respondent (week, month, year)
df$alcohol_adj = df$alcohol
df$alcohol_adj[df$alcohol_unit == "month"] = df$alcohol_adj[df$alcohol_unit == "month"] / 4.345 #divide by average weeks per month
df$alcohol_adj[df$alcohol_unit == "year"] = df$alcohol_adj[df$alcohol_unit == "year"] / 52.143 #divide by average weeks per year
```
As we have got a nice cleaned dataset, we want to visualize our data with pair plots first. As shown in the pair plots for the systolic blood pressure, specifically from the scatter plots, we can find that there are weak relations or almost no relations between the variables. Moreover, from the histograms, we can find that the all the variables seem not to be normally distributed. Athough the variable systolic blood pressure and the variable bmi approach to be normally distributed, they are still right skewed. In addition, as shown in the pair plots for the diatolic blood pressure, from the scatter plots, again, we can find that there are weak relations or almost no relations between the variables. Also, from the histograms, except that the variable diatolic blood pressure seems to be almost normally distributed (only a little bit left skewed), all the other variables are not normally distributed.
```{r preliminary analyses}
#test the assumptions for the linear regression
#assumption1) normality assumption: check if the continuous variables are normal
par( mfrow=c(3,3) )
#DVs
hist(df$SBP)
hist(df$DBP)
#IVs
hist(df$age)
hist(df$bmi)
hist(df$sleep)
hist(df$alcohol_adj)

#check the distributions
hist(df$overtime)
hist(df$SBP_bi)
hist(df$DBP_bi)
```

```{r dplyr_matrix_plot}
#for SPB
pairs(SBP ~ overtime + gender + age + bmi +
        alcohol_adj + sleep + smoke, data = df)
```
```{r dplyr_matrix_plot2}
#for DBP
pairs(DBP ~ overtime + gender + age + bmi + 
        alcohol_adj + sleep + smoke, data = df)

```

We want to check whether the following assumptions of the linear regression model are held:

1. Homoscedasticity: The variance of the residual is constant. 
2. Linearity: The relationship between between the independent and dependent variables is linear.
3. No or little multicollinearity: There is no or little collinearity between independent variables.

1. Linearity

In order to check the linearity assumption, we plotted partial regression plots for both systolic blood pressure and diatolic pressure against each of the independent variables.
```{r assumption linearity}
#assumption3) linearity
#first fit a linear regression with all covariates
avplot_SBP = lm(SBP ~ overtime + gender + age + bmi + 
                  alcohol_adj + sleep + smoke, data = df)
avplot_DBP = lm(DBP ~ overtime + gender + age + bmi + 
                  alcohol_adj + sleep + smoke, data = df)
#then see the added variable plots
car::avPlots(avplot_SBP) #for SBP
```
```{r avplots_DBP}
car::avPlots(avplot_DBP) #for DBP
```
From the partial regression plots of the systolic blood pressure, we can find that for each of the independent variable, the expected value of the dependent variable (systolic blood pressure) is indeed a straight-line function of the independent variable, holding the others fixed. Also, from the partial regression plots of the diatolic blood pressurewe, we can get the same conclusion. Therefore, the assumption of linearity can be considered as satisfied.

2. Homoscedasticity

In order to check the homoscedasticity assumption, we plotted residual plots for both systolic blood pressure and diatolic pressure.
```{r assumption Homoscedasticity SBP}
#standardized residuals plot
#SBP
SBP_red = rstandard(avplot_SBP)
fitted_SBP = avplot_SBP$fitted.values

plot(fitted_SBP, SBP_red, xlab = "Fitted Values", 
     ylab = "Standardized Residuals", 
     main = "Standardized Residuals Plot (SBP)")
```
```{r assumption Homoscedasticity DBP}
#DBP
DBP_red = rstandard(avplot_DBP)
fitted_DBP = avplot_DBP$fitted.values

plot(fitted_DBP, DBP_red, xlab = "Fitted Values", 
     ylab = "Standardized Residuals", 
     main = "Standardized Residuals Plot (DBP)")
```
From the residual plot of the systolic blood pressure, we can find the mean of the residual is almost 0, and the variance seems to be almost constant. Also, we have the same finds for the diatolic blood pressure. Therefore, the assumption of homoscedasticity can be considered as satisfied.

2. No or little multicollinearity

In order to check the no/little-multicollinearity assumption, we computed the Pearson correlations between the continuous independent variables and Chi-squared correlation test between the binary independent variables.
```{r collinearity for continuous variables}
#collinearity for continuous variables
cont_df = df %>% 
  select(age, bmi, alcohol_adj, sleep)
cor(cont_df) 
#correlation coefficients have small values

```
```{r collinearity for categorical variables}
#collinearity for categorical variables
cate_df = df %>%
  select(gender, smoke, overtime)
chisq.test(cate_df$gender, cate_df$smoke)
chisq.test(cate_df$gender, cate_df$overtime)
chisq.test(cate_df$smoke, cate_df$overtime)
#no significant associations
```
As shown in the heatmap of the correlations between the continuous independent variables, we can find that there are very small or almost no correlations between the continuous independent variables. Also, as the table of the Pearson correlations between the binary variables shows, we can find that there is little collinearity between each pair of the binary variables.

We fit our linear regression models.

For the systolic blood pressure, we fit the model: 
$$
\begin{aligned}
 y &= \beta_{0} + \beta_{workhrs}*x_{workhrs} + \beta_{gender}*x_{gender} + \beta_{age}*x_{age} + \beta_{bmi}*x_{bmi} \notag\\
 &+ \beta_{sleep}*x_{sleep} + \beta_{smoke}*x_{smoke} + \beta_{avg\_alcohol\_freq\_wk}*x_{avg\_alcohol\_freq\_wk} + \epsilon
\end{aligned}
$$

And for diatolic blood pressure, we fit the model: 
$$
\begin{aligned}
 y &= \beta_{0} + \beta_{workhrs}*x_{workhrs} + \beta_{gender}*x_{gender} + \beta_{age}*x_{age} + \beta_{bmi}*x_{bmi} \notag\\
 &+ \beta_{sleep}*x_{sleep} +  \beta_{smoke}*x_{smoke} + \beta_{avg\_alcohol\_freq\_wk}*x_{avg\_alcohol\_freq\_wk} + \epsilon
\end{aligned}
$$
```{r modeling SBP}
#core analysis ----------------------------------------------
#linear regression with "overtime" as the main predictor
model_SBP = gls(SBP ~ overtime + gender + age + bmi + 
                  alcohol_adj + sleep + smoke, data = df)
summary(model_SBP)
```
```{r modeling DBP}
model_DBP = gls(DBP ~ overtime + gender + age + bmi + 
                  alcohol_adj + sleep + smoke, data = df)
summary(model_DBP)
```

From the summary results of the linear regression model for the systolic blood pressure, we can find that although the coefficient of the working hours is positive, which implies that working overtime increases the risk of high systolic blood pressure, this effect is not significant ($\beta = 1.58$, p = 0.557). As a result, we can conclude that working overtime cannot lead to abnormal systolic blood pressure. Besides, from the summary results of the linear regression model for the diatolic blood pressure, we can find that although the coefficient of the working hours is positive as well, which implies that working overtime increases the risk of high diatolic blood pressure too, this effect is not significant as well($\beta = 0.2246$, p = 0.905). As a result, we can conclude that working overtime also cannot lead to abnormal diatolic blood pressure. Therefore, in conclusion, working overtime also cannot lead to abnormal blood pressure.

```{r additional analysis SBP} 
#logistic regression with normal vs. abnormal BP outcome
logistic_SBP <- glm(SBP_bi ~ overtime + gender + age + bmi + 
                      alcohol_adj + sleep + smoke,
                    family = binomial(link = 'logit'),
                    data = df)
summary(logistic_SBP)
```
```{r additional analysis DBP} 
logistic_DBP <- glm(DBP_bi ~ overtime + gender + age + bmi + 
                      alcohol_adj + sleep + smoke,
                    family = binomial(link = 'logit'),
                    data = df)
summary(logistic_DBP)
```

### Python
```{r html setup}
htmltools::includeHTML("Tian_506_Project.html")
```

##